cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Added pyramid overall paragraph

>>>>

A pyramid structure represents data arranged around a central apex and base, useful for exploring how algorithms handle pointed or layered geometries in high-dimensional space. The functions provided allow users to generate pyramids with various base shapes—including rectangular, triangular, and star-shaped bases—with options for sharp or blunted apexes. Additionally, we offer functionality for creating pyramids containing structured holes, enabling the study of non-convex and sparse regions. These designs are valuable for testing the ability of dimension reduction and clustering algorithms to preserve and detect complex geometric features. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:pyramid-tb-html)', '\\@ref(tab:pyramid-tb-pdf)'))` summarizes these functions.

### 2025-06-24 paper-cardinalR.tex
Added pyramid overall paragraph

>>>>

A pyramid structure represents data arranged around a central apex and base, useful for exploring how algorithms handle pointed or layered geometries in high-dimensional space. The functions provided allow users to generate pyramids with various base shapes---including rectangular, triangular, and star-shaped bases---with options for sharp or blunted apexes. Additionally, we offer functionality for creating pyramids containing structured holes, enabling the study of non-convex and sparse regions. These designs are valuable for testing the ability of dimension reduction and clustering algorithms to preserve and detect complex geometric features. Table \ref{tab:pyramid-tb-pdf} summarizes these functions.
